An OSGi-based Sensor Network for \\ Environmental Monitoring

### 2009-02-16 docs/icccn2009/paper.tex
First stab at an outline
git-svn-id: svn://localhost/netbeams/trunk@296 559edde2-a4d4-44e0-96fc-4035e40d7396

The introduction.

>>>>

The introduction should emphasize that we interpret sensor networks in
a different way: our focus is on off-the-shelf, highly specialized
sensors for environmental monitoring. Our focus is end-to-end: how to
collect data from a remote location with no stationary power or
Internet connection and deliver the data in near-realtime to a web
browser. Length: first page (including title and abstract).

\section{Use Case}

Start with some related work. Who else has done an OSGi-based
infrastructure for sensor networks? Kleber: I believe you have a few
references. This section should be a combination of a use case (using
the RTC and their YSI sonde as an example) and a requirements
analysis: requirements such as remote management and monitoring
capabilities, time-delayed communication, etc. In this section should
be no mentioned of DSP or OSGi. Length: 1 page.

\section{DSP}

Should describe the OSGi-based NetBEAMS architecture. Total length of
this section: 2 pages.

\subsection{Data Sensor Framework and Platform}

should include a picture of a standalone DSP showing a DC and a DP
(general description only). Explain difference between DSP Framework
and DSP Platform. This section should give a top-level overview.
Subsequent sub-sections should explain certain features of the DSP in
more detail.

\subsection{DP and DC}

Should give some API sniplets for DP and DC.

\subsection{DSP Message}

Should explain the way DSP Messages are defined: XML Schema and JAXB.

\subsection{Matcher}

\section{NetBEAMS}

Should explain some specific DC and DP we have implemented for
NetBEAMS. Length: 1 - 1.5 pages.

\subsection{YSI Sonde DP}

\subsection{Wire transport DC/DP}

\subsection{Web Managements}

\section{Conclusions and Outlook}

Length (including bibliography): 0.5 pages.
